Nirdizati: A Web-Based Tool for\\ Predictive Process Monitoring

### 2017-07-25 BPM17-demo-paper/paper.tex

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\textwidth]{img/dfd_0}
	\caption{High-level data flow diagram of Nirdizati Runtime.}
	\label{fig:dfd_0}
\end{figure}
\vspace{-\baselineskip}

When a user logs into the system, she initially sees a table listing both currently ongoing cases (colored in gray) as well as completed cases (colored in green), as shown in \figurename~\ref{fig:nirdizati-runtime}. For each case, Nirdizati Runtime provides a range of summary statistics including the number of events in a given case, starting time of a case and the time when the latest event has occurred. For the ongoing cases, Nirdizati Runtime also estimates their completion time and a range of other process-specific indicators, such as the probability that a customer will not accept an offer from a salesperson. For completed cases, instead, it shows the actual completion time and the actual values of the indicators.

@@

\section{Conclusion} \label{sec:conclusion}
Nirdizati is a configurable full-stack web application that supports users in selecting the preferred prediction method from a list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
The results of the predictions, as well as the real-time summary statistics about the process executions, are presented in a dashboard that offers multiple visualization options.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\textwidth]{img/dfd_0}
	\caption{High-level data flow diagram of Nirdizati Runtime.}
	\label{fig:dfd_0}
\end{figure}
%\vspace{-\baselineskip}

When a user logs into the system, she initially sees a table listing both currently ongoing cases (colored in gray) as well as completed cases (colored in green), as shown in \figurename~\ref{fig:nirdizati-runtime}. For each case, Nirdizati Runtime provides a range of summary statistics including the number of events in the case, its starting time and the time when the latest event in the case has occurred. For the ongoing cases, Nirdizati Runtime also estimates their completion time and a range of other process-specific indicators, such as the probability that a customer will not accept an offer from a salesperson. For completed cases, instead, it shows the actual completion time and the actual values of the indicators.

@@

\section{Conclusion} \label{sec:conclusion}
Nirdizati is a configurable full-stack web application that supports users in building and selecting a set of predictive models and, based on these models, it enables the continuous prediction of various performance indicators at runtime.
The results of the predictions, as well as the real-time summary statistics about the process executions, are presented in a dashboard that offers multiple visualization options.
